### 2020-01-26 introduction.tex
fixes

Mutation testing \cite{demillo1978hints,budd1980theoretical} (or mutation analysis, the term we will use in this work, for reasons that will become clear) uses small syntactic changes to a program to introduce synthetic ``faults,'' under the assumption that if the original version of a program is (mostly) correct, most small changes will therefore introduce a fault.  For the most part, mutation analysis has been used to evaluate test suites by computing a score (the ratio of mutants the suite detects, or ``kills'').  Most such use has been in research efforts, rather than practical testing efforts, though there has been sporadic use by interested developers.
In an ASE 2015 \cite{groce2015verified} paper and a 2018 journal extension \cite{groce2018verified} of that paper, Groce et al. proposed examining individual mutants that survive a formal verification or automated test generation process to detect and correct weaknesses in a specification or test generator.  The approach was able to expose bugs in a heavily-tested module of the Linux kernel \cite{mutKernel} and improve a heavily used test generator for the {\tt pyfakefs} file system.  Recently, mutation analysis has been adopted in industrial settings, though not for actual examination of all surviving mutants \cite{MutGoogle,ivankovic2018industrial}, a practice that is hard to scale to large code bodies.

@@

The value of the differential comparison lies in a few key points.  First, this is a measure that does not reward a tool that produces too many false positives.  The tool cannot simply flag all code as having a problem or it will perform poorly at the task of \emph{distinguishing} the mutated code from non-mutated (and presumably at least \emph{more} correct) code.  Based on verification and testing uses of mutation, it is safe to say that usually at minimum 40\%, often 50-60\%, and frequently up to 80\%+ \cite{mutKernel,groce2018verified}, of mutants are not semantically equivalent to the original code, and are actually fault-inducing \cite{TCE,impactEquiv,smith2009should}, so the task presented to a static analysis tool is the generalization of the task we ideally expect static analysis to perform:  to identify faulty code, without executing it, and, most critically, \emph{to distinguish faulty from correct code}.  Obviously, many faults cannot be identified statically without a complete specification, or without unreasonable analysis cost and precision, but the measure of performance here is meant to be mostly \emph{relative} to other tools applied to the same code; this is primarily a \emph{differential} approach.  In other words, a key notion is that while most mutants cannot be detected statically, the ones that are tend to be \emph{true positives}: if they were real code changes, they would be faults.

>>>>

Mutation testing \cite{jia2011analysis,demillo1978hints,budd1980theoretical} (or mutation analysis, the term we will use in this work, for reasons that will become clear) uses small syntactic changes to a program to introduce synthetic ``faults,'' under the assumption that if the original version of a program is (mostly) correct, most small changes will therefore introduce a fault.  For the most part, mutation analysis has been used to evaluate test suites by computing a score (the ratio of mutants the suite detects, or ``kills'').  Most such use has been in research efforts, rather than practical testing efforts, though there has been sporadic use by interested developers.
In an ASE 2015 \cite{groce2015verified} paper and a 2018 journal extension \cite{groce2018verified} of that paper, Groce et al. proposed examining individual mutants that survive a formal verification or automated test generation process to detect and correct weaknesses in a specification or test generator.  The approach was able to expose bugs in a heavily-tested module of the Linux kernel \cite{mutKernel} and improve a heavily used test generator for the {\tt pyfakefs} file system.  Recently, mutation analysis has been adopted in industrial settings, though not for actual examination of all surviving mutants \cite{MutGoogle,ivankovic2018industrial}, a practice that is hard to scale to large code bodies.

@@

The value of the differential comparison lies in a few key points.  First, this is a measure that does not reward a tool that produces too many false positives.  The tool cannot simply flag all code as having a problem or it will perform poorly at the task of \emph{distinguishing} the mutated code from non-mutated (and presumably at least \emph{more} correct) code.  Based on verification and testing uses of mutation, it is safe to say that usually at minimum 40\%, often 50-60\%, and frequently up to 80\%+ \cite{mutKernel,groce2018verified,le2014mucheck}, of mutants are not semantically equivalent to the original code, and are actually fault-inducing and detectable by some test or property \cite{TCE,impactEquiv,smith2009should}, so the task presented to a static analysis tool is the generalization of the task we ideally expect static analysis to perform:  to identify faulty code, without executing it, and, most critically, \emph{to distinguish faulty from correct code}.  Obviously, many faults cannot be identified statically without a complete specification, or without unreasonable analysis cost and precision, but the measure of performance here is meant to be mostly \emph{relative} to other tools applied to the same code; this is primarily a \emph{differential} approach.  In other words, a key notion is that while most mutants cannot be detected statically, the ones that are tend to be \emph{true positives}: if they were real code changes, they would be faults.

### 2020-01-26 relatedwork.tex
fixes

Finally, the large body of work on using mutants in software testing \cite{demillo1978hints,budd1980theoretical, groce2015verified,groce2018verified,MutGoogle,ivankovic2018industrial,mutKernel} is obviously relevant, in that we basically adopt its approach, but re-define killing a mutation for a static analysis context.  Methods for improving mutation analysis in testing will often (but not always, e.g. those based on coverage or other dynamic information) transfer to our context as well.

>>>>

Finally, the large body of work on using mutants in software testing \cite{jia2011analysis,demillo1978hints,budd1980theoretical, groce2015verified,groce2018verified,MutGoogle,ivankovic2018industrial,mutKernel} is obviously relevant, in that we basically adopt its approach, but re-define killing a mutation for a static analysis context.  Methods for improving mutation analysis in testing will often (but not always, e.g. those based on coverage or other dynamic information) transfer to our context as well.
